---
title: "Hands-on Exercise 5"
author: "Thet Myat Noe"
date: "April 30, 2024"
date-modified: "last-modified"
execute:
  eval: true
  echo: true
  warning: false
  freeze: true
---

# **Visualising and Analysing Text Data with R: tidytext methods**

## 29.1 Learning Outcome

In this hands-on exercise, we will learn how to visualise and analyse text data using R.

By the end of this hands-on exercise, we will be able to:

-   understand tidytext framework for processing, analysing and visualising text data,

-   write function for importing multiple files into R,

-   combine multiple files into a single data frame,

-   clean and wrangle text data by using tidyverse approach,

-   visualise words with Word Cloud,

-   compute term frequency–inverse document frequency (TF-IDF) using tidytext method, and

-   visualising texts and terms relationship.

## 29.2 Getting Started

### 29.2.1 Installing and launching R packages

In this hands-on exercise, the following R packages for handling, processing, wrangling, analysing and visualising text data will be used:

-   tidytext, tidyverse (mainly readr, purrr, stringr, ggplot2)

-   widyr,

-   wordcloud and ggwordcloud,

-   textplot (required igraph, tidygraph and ggraph, )

-   DT,

-   lubridate and hms.

The code chunk:

```{r}
pacman::p_load(tidytext, widyr, wordcloud, DT, ggwordcloud, textplot, lubridate, hms, tidyverse, tidygraph, ggraph, igraph)
```

## 29.3 Importing Multiple Text Files from Multiple Folders
### 29.3.1 Creating a folder list

```{r}
news20 <- "/data/20news/"
```

### 29.3.2 Define a function to read all files from a folder into a data frame
```{r}
read_folder <- function(infolder) {
  tibble(file = dir(infolder, 
                    full.names = TRUE)) %>%
    mutate(text = map(file, 
                      read_lines)) %>%
    transmute(id = basename(file), 
              text) %>%
    unnest(text)
}
```

## 29.4 Importing Multiple Text Files from Multiple Folders
### 29.4.1 Reading in all the messages from the 20news folder
```{r}

```
